Collective behavior of Janus Particles Suspended in a Viscous Fluid

### 2022-08-04 doc/PRF2022/PRF_main.tex
yny

In this work, we employ the newly developed JP model using BIEs ~\cite{Fu20, Fu2022_JFM} 
and tune the boundary conditions with energy normalization to study the dynamics of 
amphiphilic (BC(i)), biased hydrophobic (BC (ii)), and bipolar (BC(iii)) JPs.
To overcome the well-known 
obstacle for numerical implementations in the free energy $F$ where the gradient of 
solution to the screened Laplace equation involves hyper-singularities, we derive the normal 
derivative \eqref{eq:normal_deriv} in terms of single layer potential $\SSS$.

@@

% If you have acknowledgments, this puts in the proper section head.
\begin{acknowledgments}
We thank Dr.~S\'ebastien Michelin and Dr.~Cecile Cottin-Bizzonne from LadHyX - Ecole Polytechnique Institut Polytechnique de Paris for organizing the focus-session ``interfacial active matter'' in the conference APS-DFD 2021 and the invitation of submitting a special collection paper.

>>>>

In this work, we employ the newly developed JP model using BIEs ~\cite{Fu20, Fu2022_JFM} 
and tune the boundary conditions with energy normalization to study the  collective dynamics of 
amphiphilic (BC(i)), biased hydrophobic (BC (ii)), and bipolar (BC(iii)) JPs under various flowing conditions (quiescent, linear shear flow, and Taylor-Green flow).
Three quantities are computed to characterize the dynamics of the collective configurations of JPs: Free energy $F$, strain parameter $E$ and 
scalar order parameter $S_2$.

To overcome the well-known 
obstacle for numerical implementations in the free energy $F$ where the gradient of 
solution to the screened Laplace equation involves hyper-singularities, we derive the normal 
derivative \eqref{eq:normal_deriv} in terms of single layer potential $\SSS$.

@@

% If you have acknowledgments, this puts in the proper section head.
\begin{acknowledgments}
We thank Dr.~S\'ebastien Michelin and Dr.~Cecile Cottin-Bizzonne from LadHyX - Ecole Polytechnique Institut Polytechnique de Paris for organizing the focus-session ``interfacial active matter'' in the conference APS-DFD 2021 and the invitation of submitting a special collection paper. 
B.Q. acknowledges support from the Simons Foundation, Mathematics and Physical Sciences-Collaboration Grants for Mathematicians, Award No. 527139.
Y.-N.Y. acknowledges support from NSF (Grants No. DMS 1614863 and No. DMS 195160) and Flatiron Institute, part of Simons Foundation.
